Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-06 paper/background.tex
Paper update
Add figure

\textcolor{red}{TODO: If there is still space, illustrate the objecive with the PM-width figure}

\begin{figure}[]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/PM.eps}}
        \caption{Phase margin of an amplifier as function of the width of a transistor}
        \label{fig:PMOpAmp}
    \end{center}
\end{figure}

@@

@@

The LCB function is defined as follows:
\begin{equation}
    \label{eq:LCB}
    \mathrm{LCB}(\bm{x}) = \mu(\bm{x}) - \kappa \sigma(\bm{x})
\end{equation}
Where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP. $\kappa$ is a parameter that balances the exploitation and exploration.

Following the suggestion of~\cite{brochu2010tutorial}, the $\kappa$ in \eqref{eq:LCB} is defined as:
\begin{equation}
    \label{eq:LCBKappa}
    \begin{array}{lll}
        \kappa &=& \sqrt{\nu \tau_t} \\
        \tau_t &=& 2 \log(t^{d/2+2} \pi^2 / 3 \delta)
    \end{array}
\end{equation}
where $t$ is the number of current iteration. $\nu$ and $\delta$ are two user-defined parameters, we fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.

The PI and EI function are defined as
\begin{equation}
    \label{eq:PI_EI}
    \begin{array}{lll}
        \mathrm{PI}(\bm{x}) &=& \Phi(\lambda) \\
        \mathrm{EI}(\bm{x}) &=& \sigma(\bm{x}) (\lambda \Phi(\lambda) + \phi(\lambda))     \\
        \mathrm{\lambda}    &=& \displaystyle \frac{\tau - \xi - \mu(\bm{x})}{\sigma(\bm{x})}, 
    \end{array}
\end{equation}
where $\tau$ is the current best value objective value, and $\xi$ is a small positive jitter to improvement the ability of exploration. The $\Phi(.)$ and $\phi(.)$ functions are the CDF and PDF functions of normal distribution.

@@

There are also other acquisition functions, like the knowledge gradient~\cite{scott2011correlated} function, predictive entropy search~\cite{hernandez2014predictive}. A portfolio of several acquisition functions is also possible~\cite{hoffman2011portfolio}.

>>>>

% \textcolor{red}{TODO: If there is still space, illustrate the objecive with the PM-width figure}

% \begin{figure}[]
%     \begin{center}
%         \centerline{\includegraphics[width=\columnwidth]{./img/PM.eps}}
%         \caption{Phase margin of an amplifier as function of the width of a transistor}
%         \label{fig:PMOpAmp}
%     \end{center}
% \end{figure}

@@

\textcolor{red}{$\sigma_f$ ???}

@@

The LCB function is defined as follows:
\begin{equation}
    \label{eq:LCB}
    \mathrm{LCB}(\bm{x}) = \mu(\bm{x}) - \kappa \sigma(\bm{x})
\end{equation}
Where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP, $\kappa$ is a parameter that balances the exploitation and exploration.

Following the suggestion of~\cite{brochu2010tutorial}, the $\kappa$ in \eqref{eq:LCB} is defined as:
\begin{equation}
    \label{eq:LCBKappa}
    \begin{array}{lll}
        \kappa &=& \sqrt{\nu \tau_t} \\
        \tau_t &=& 2 \log(t^{d/2+2} \pi^2 / 3 \delta),
    \end{array}
\end{equation}
where $t$ is the number of current iteration, $\nu$ and $\delta$ are two user-defined parameters. We fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.

The PI and EI function are defined as
\begin{equation}
    \label{eq:PI_EI}
    \begin{array}{lll}
        \mathrm{PI}(\bm{x}) &=& \Phi(\lambda) \\
        \mathrm{EI}(\bm{x}) &=& \sigma(\bm{x}) (\lambda \Phi(\lambda) + \phi(\lambda))     \\
        \mathrm{\lambda}    &=& \displaystyle \frac{\tau - \xi - \mu(\bm{x})}{\sigma(\bm{x})}, 
    \end{array}
\end{equation}
where $\tau$ is the current best value objective value, and $\xi$ is a small positive jitter to improvement the ability of exploration. The $\Phi(.)$ and $\phi(.)$ functions are the CDF and PDF functions of normal distribution. We fix $\xi = 1e-3$ in our implementation of the MACE algorithm.

@@

There are also other acquisition functions, like the knowledge gradient~\cite{scott2011correlated} function, predictive entropy search~\cite{hernandez2014predictive}, and the max-value entropy search\cite{wang2017max}. A portfolio of several acquisition functions is also possible~\cite{hoffman2011portfolio}.

### 2018-02-06 paper/mace.tex
Add figure

@@

Unlike single-objective optimization, multi-objective optimization problems
simultaneously optimize multiple objectives~\cite{MO_overview}, the
multi-objective optimization problem is formulated as
\begin{equation}
    \label{eq:MOFormulation}
    \begin{aligned}
        & \text{minimize} & & f_1(\bm{x}),~\dots~,f_m(\bm{x})
    \end{aligned}
\end{equation}
When we have multiple objectives to optimizes, the objectives can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives, the goal of multi-objective optimization algorithms is to appropriate the \emph{Pareto front} of the objectives. A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$. A design is \emph{Pareto-optimal} if it is not dominated by any other point in the design space and dominate at least one point. The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}. It is often unlikely to get the whole Pareto front as there might be infinite points on the front, the goal of multi-objective optimization is to find a set of designs that approximates the true Pareto front.

There exist many mature multi-objective optimization algorithms, like the
non-dominated sorting based genetic algorithm (NSGA-II)~\cite{nsgaii}, and the
multi-objective evolutionary algorithm based on decomposition
(MOEA/D)~\cite{moead}. In this paper, the multi-objective optimization based on
differential evolution (DEMO)~\cite{demo} is used to solve multi-objective
optimization problems.

% When we have more than one objective to optimize, the problem is formulated as:

@@

We propose a novel heuristic for the parallelization of Bayesian optimization.
The parallelization is realized via the multi-objective ensemble of multiple
acquisition functions. As each acquisition function represents a unique
interpretation to the optimization problem, different acquisition functions may
not agree with each other about where to sample the next point. For example,
the value of LCB function always decreases as the $\sigma(\bm{x})$ increases,
however, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI
would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) >
\tau$. For a noise-free problem, the EI values at already sampled points are
always zero, so that any unsampled point would have a better EI value than the
sampled points, while this property does not hold for the LCB function.

\textcolor{red}{TODO: Illustrate PF}
\begin{figure}[ht]
    \vskip 0.2in
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/pf.jpg}}
        \caption{Illustration of Pareto front}
        \label{fig:PF_example}
    \end{center}
    \vskip -0.2in
\end{figure}

>>>>

\begin{figure*}[tp!]
    \centering
    \subfigure[True phase margin curve, GP predictions, and Pareto set]{\label{fig:PF_example_1}\includegraphics[width=0.49\textwidth]{./img/pm_gp_ps.eps}}
    ~
    \subfigure[The LCB, EI, and PI functions and the Pareto front]{\label{fig:PF_example_1}\includegraphics[width=0.49\textwidth]{./img/pf.eps}}
    \caption{Illustration of the multi-objective optimization of acquisition functions}
    \label{fig:PF_example}
        % \begin{subfigure}[]{width=0.5\textwidth}
        %     \includegraphics[width=0.5\textwidth]{./img/pf.eps}
        %     \caption{LCB, EI, PI and PF}
        %     \label{fig:PF_example_1}
        % \end{subfigure}
        % \begin{subfigure}[]{0.5\textwidth}
        %     \includegraphics[width=0.5\textwidth]{./img/pm_gp_ps.eps}
        %     \caption{True curve, GP predictions and PS}
        %     \label{fig:PF_example_1}
        % \end{subfigure}
\end{figure*}

@@

Unlike single-objective optimization, there are multiple objectives to optimize in multi-objective optimization problems\cite{MO_overview}, the multi-objective optimization problem is formulated as
\begin{equation}
    \label{eq:MOFormulation}
    \begin{aligned}
        & \text{minimize} & & f_1(\bm{x}),~\dots~,f_m(\bm{x}).
    \end{aligned}
\end{equation}
The multiple objectives to be optimizes can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives, the goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives. A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$. A design is \emph{Pareto-optimal} if it is not dominated by any other point in the design space and dominate at least one point. The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}. It is often unlikely to get the whole Pareto front as there might be infinite points on the front, the goal of multi-objective optimization is to find a set of designs that approximates the true Pareto front.

There exist many mature multi-objective optimization algorithms, like the non-dominated sorting based genetic algorithm (NSGA-II)~\cite{nsgaii}, and the multi-objective evolutionary algorithm based on decomposition (MOEA/D)~\cite{moead}. In this paper, the multi-objective optimization based on differential evolution (DEMO)~\cite{demo} is used to solve multi-objective optimization problems, but other multi-objective optimization algorithms can also be applied.

@@

Each acquisition function represents a unique selection strategy, different acquisition functions may not agree with each other about where to sample the next point. For example, the value of LCB function always decreases as the $\sigma(\bm{x})$ increases, however, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) > \tau$. For a noise-free problem, the EI values at already sampled points would always be lower than any unsampled location, while this property does not hold for the LCB function.
